Understanding the Lomb-Scargle Periodogram

### 2017-01-05 PracticalLombScargle.tex
Add eclipsing binary example

A further generalization involves multi-term Fourier models at each frequency:
rather than fitting just a single sinusoid at each frequency, we might fit a
partial Fourier series at each frequency:
\begin{equation}
  y_{model}(t;f) = y^{0}_f + \sum_{k=1}^K A_f^{(k)} \sin(2\pi k f (t - \phi_f^{(k)})).
\end{equation}
This type of multi-term Lomb-Scargle periodogram was studied in detail by
\citet{Bretthorst88}.

This kind of multiterm generalization is quite tempting, because it means that
the periodogram can fit models that are more complicated than

\todo{Show performance on eclipsing data}

@@

\section{Generalizations \& Challenges}
\sectlabel{generalizations}

\begin{itemize}
\item floating-mean
\item Uncertainties in Data
\item Bayesian view is (almost always) not useful
\item Multiterm makes the true period fit better, but also bumps the background noise.
\end{itemize}

>>>>

A further generalization involves multi-term Fourier models at each frequency:
rather than fitting just a single sinusoid at each frequency, we might fit a
partial Fourier series at each frequency, adding $K$ additional components at
integer multiples of the fundamental frequency:
\begin{equation}
  y_{model}(t;f) = y^{0}_f + \sum_{k=1}^K A_f^{(k)} \sin(2\pi k f (t - \phi_f^{(k)})).
\end{equation}
This type of multi-term Lomb-Scargle periodogram was studied in detail by
\citet{Bretthorst88}.

This kind of Fourier series generalization to the periodogram is quite
tempting, because it means that the periodogram can be tuned to fit models
that are more complicated than simple sine waves.
\citet{Bretthorst88} takes this even further, exploring applications to
decaying signals and other more complex models.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig23_binary_multiterm}
  \caption{1-term and 6-term Lomb-Scargle models fit to LINEAR object
    14752041, an eclipsing binary. Notice that the standard periodogram
    (top panels) finds an alias of the true 17.5-hour frequency,
    because a simple sinusoidal model cannot closely fit both the primary
    and secondary eclipse. A six-term Fourier model (bottom panels), on
    the other hand, does find the true period.
    \figlabel{binary-multiterm}}
\end{figure}

@@
